Seniors remain the most vulnerable population group as Toronto enters the 6th wave of COVID-19

### 2022-04-23 outputs/paper/paper.Rmd
Finalize paper

```{r data, include=FALSE}
covid_data <- read_csv("../../outputs/data/covid_data.csv")
```

@@

As shown in figure \@ref(fig:outbreak-associated), most COVID-19 cases are sporadic without any outbreak-associated. This is interesting because we can tell most COVID-19 cases might not be related to any outbreak associated with a gathering of people. Rather, people might get COVID-19 without going to a place that has been later identified as a sight that caused most people to get sick. Combining with the insight that we can get from \@ref(fig:source-of-infection), there is a significant number of COVID-19 cases that do not have any information on their sources of infection. This shows that there might be a portion of people who were in the sporadic infection category who did not any information about how they got COVID-19.

```{r outbreak-associated, echo=FALSE, fig.cap='Outbreak Associated'}
# Create bar plot for age group
ggplot(data=covid_data, aes(x=outbreak_associated, fill=outbreak_associated)) + 
  geom_bar(stat="count") +
  xlab('Outbreak Associated') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r source-of-infection, echo=FALSE, fig.cap='Source of Infection'}
# Create bar plot for age group
ggplot(data=covid_data, aes(x=source_of_infection, fill=source_of_infection)) + 
  geom_bar(stat="count") +
  xlab('Source of Infection') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

@@

Community Contact is the most common source of infection as shown in \@ref(fig:source-of-infection). Most COVID-19 cases spread the virus to the people in their community since they might interact the most with people who are close to them. It is also worthy to point out that there are a significant number of COVID-19 cases that could not identify how they got infected with COVID-19. Since it is hard to pinpoint an exact time and place of how people got COVID-19 and most COVID-19 cases are sporadic, it is indeed hard for people to identify where exactly they got COVID-19. This also reflects how important it is for people to have COVID-19 exposure apps on their phones so that they can be alerted if they ever came across someone who had COVID-19 at least.

@@

```{r community-age-group, echo=FALSE, fig.cap='Community Infection by Age Group'}
community_data <- covid_data %>%
  filter(source_of_infection=="Community")

# Create bar plot for age group
ggplot(data=community_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Community Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r healthcare-institutions-age-group, echo=FALSE, fig.cap='Healthcare Institutions Infection by Age Group'}
healthcare_institutions_data <- covid_data %>%
  filter(source_of_infection=="Outbreaks, Healthcare Institutions")

# Create bar plot for age group
ggplot(data=healthcare_institutions_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Healthcare Institutions Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r household-contact-group, echo=FALSE, fig.cap='Household Contact Infection by Age Group'}
household_contact_data <- covid_data %>%
  filter(source_of_infection=="Household Contact")

# Create bar plot for age group
ggplot(data=household_contact_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Household Contact Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r close-contact-group, echo=FALSE, fig.cap='Close Contact Infection by Age Group'}
close_contact_data <- covid_data %>%
  filter(source_of_infection=="Close Contact")

# Create bar plot for age group
ggplot(data=close_contact_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Close Contact Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r congregate-settings-group, echo=FALSE, fig.cap='Congregate Settings Infection by Age Group'}
congregate_settings_data <- covid_data %>%
  filter(source_of_infection=="Outbreaks, Congregate Settings")

# Create bar plot for age group
ggplot(data=congregate_settings_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Congregate Settings Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r travel-group, echo=FALSE, fig.cap='Travel Infection by Age Group'}
travel_data <- covid_data %>%
  filter(source_of_infection=="Travel")

# Create bar plot for age group
ggplot(data=travel_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Travel Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

@@

```{r fatal-age-group, echo=FALSE, fig.cap='Fatality by Age Group'}
fatal_data <- covid_data %>%
  filter(outcome=="FATAL")

# Create bar plot for age group
ggplot(data=fatal_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Fatality by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

@@

```{r gender, echo=FALSE, fig.cap='Gender'}
# Create bar plot for age group
ggplot(data=covid_data, aes(x=client_gender, fill=client_gender)) + 
  geom_bar(stat="count") +
  xlab('Gender') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r reported-date, echo=FALSE, fig.cap='Reported Date'}
# Create bar plot for age group
ggplot(data=covid_data, aes(x=reported_date)) + 
  geom_line(stat="count") +
  xlab('Reported Date') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r fatal-gender, echo=FALSE, fig.cap='Fatality by Gender'}
fatal_data <- covid_data %>%
  filter(outcome=="FATAL")

# Create bar plot for age group
ggplot(data=fatal_data, aes(x=client_gender, fill=client_gender)) + 
  geom_bar(stat="count") +
  xlab('Fatality by Gender') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

>>>>

```{r data, include=FALSE}
# read data
covid_data <- read_csv("../../outputs/data/covid_data.csv")
```

@@

As shown in figure \@ref(fig:outbreak-associated), most COVID-19 cases are sporadic without any outbreak-associated. This is interesting because we can tell most COVID-19 cases might not be related to any outbreak associated with a gathering of people. Rather, people might get COVID-19 without going to a place that has been later identified as a sight that caused most people to get sick. Combining with the insight that we can get from figure \@ref(fig:source-of-infection), there is a significant number of COVID-19 cases that do not have any information on their sources of infection. This shows that there might be a portion of people who were in the sporadic infection category who did not any information about how they got COVID-19.

```{r outbreak-associated, echo=FALSE, fig.cap='Outbreak Associated'}
# Create bar plot for outbreak associated
ggplot(data=covid_data, aes(x=outbreak_associated, fill=outbreak_associated)) + 
  geom_bar(stat="count") +
  xlab('Outbreak Associated') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r source-of-infection, echo=FALSE, fig.cap='Source of Infection'}
# Create bar plot for source of infection
ggplot(data=covid_data, aes(x=source_of_infection, fill=source_of_infection)) + 
  geom_bar(stat="count") +
  xlab('Source of Infection') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

@@

Community Contact is the most common source of infection as shown in figure \@ref(fig:source-of-infection). Most COVID-19 cases spread the virus to the people in their community since they might interact the most with people who are close to them. It is also worthy to point out that there are a significant number of COVID-19 cases that could not identify how they got infected with COVID-19. Since it is hard to pinpoint an exact time and place of how people got COVID-19 and most COVID-19 cases are sporadic, it is indeed hard for people to identify where exactly they got COVID-19. This also reflects how important it is for people to have COVID-19 exposure apps on their phones so that they can be alerted if they ever came across someone who had COVID-19 at least.

@@

```{r community-age-group, echo=FALSE, fig.cap='Community Infection by Age Group'}
# Filter community infection data
community_data <- covid_data %>%
  filter(source_of_infection=="Community")

# Create bar plot for community infection
ggplot(data=community_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Community Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r healthcare-institutions-age-group, echo=FALSE, fig.cap='Healthcare Institutions Infection by Age Group'}
# Filter healthcare institutions infection data
healthcare_institutions_data <- covid_data %>%
  filter(source_of_infection=="Outbreaks, Healthcare Institutions")

# Create bar plot for healthcare institutions
ggplot(data=healthcare_institutions_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Healthcare Institutions Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r household-contact-group, echo=FALSE, fig.cap='Household Contact Infection by Age Group'}
# Filter household infection data
household_contact_data <- covid_data %>%
  filter(source_of_infection=="Household Contact")

# Create bar plot for household infection
ggplot(data=household_contact_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Household Contact Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r close-contact-group, echo=FALSE, fig.cap='Close Contact Infection by Age Group'}
# Filter close contact data
close_contact_data <- covid_data %>%
  filter(source_of_infection=="Close Contact")

# Create bar plot for close contact infection
ggplot(data=close_contact_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Close Contact Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r congregate-settings-group, echo=FALSE, fig.cap='Congregate Settings Infection by Age Group'}
# Filter congregate setting data
congregate_settings_data <- covid_data %>%
  filter(source_of_infection=="Outbreaks, Congregate Settings")

# Create bar plot for congregate setting infection
ggplot(data=congregate_settings_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Congregate Settings Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r travel-group, echo=FALSE, fig.cap='Travel Infection by Age Group'}
# Filter travel data
travel_data <- covid_data %>%
  filter(source_of_infection=="Travel")

# Create bar plot for travel infection data
ggplot(data=travel_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Travel Infection by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

@@

```{r fatal-age-group, echo=FALSE, fig.cap='Fatality by Age Group'}
# Filter fata cases
fatal_data <- covid_data %>%
  filter(outcome=="FATAL")

# Create bar plot for fatality by age group
ggplot(data=fatal_data, aes(x=age_group, fill=age_group)) + 
  geom_bar(stat="count") +
  xlab('Fatality by Age Group') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

@@

```{r gender, echo=FALSE, fig.cap='Gender'}
# Create bar plot for gender
ggplot(data=covid_data, aes(x=client_gender, fill=client_gender)) + 
  geom_bar(stat="count") +
  xlab('Gender') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r reported-date, echo=FALSE, fig.cap='Reported Date'}
# Create bar plot for reported date
ggplot(data=covid_data, aes(x=reported_date)) + 
  geom_line(stat="count") +
  xlab('Reported Date') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```

```{r fatal-gender, echo=FALSE, fig.cap='Fatality by Gender'}
# Filter fatal data
fatal_data <- covid_data %>%
  filter(outcome=="FATAL")

# Create bar plot for fatality by gender
ggplot(data=fatal_data, aes(x=client_gender, fill=client_gender)) + 
  geom_bar(stat="count") +
  xlab('Fatality by Gender') +
  ylab('Number of Cases') +
  theme(axis.text.x = element_text(angle = 45, hjust=1), legend.position = 'none')
```
